%-------------------------
% Resume in Latex
% Author : Matthew Sheehan
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

%------------------------
% Default tex font is Computer Modern Roman, no pkg needed

%\usepackage{fontspec}						% only for XeLaTeX
%\setmainfont{Helvetica}
%\defaultfontfeatures{Ligatures=TeX}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingMultiline}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingWorkplace}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingPosition}[2]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://mattsheehan.dev/}{\Large Matthew Sheehan}} & Email : \href{mailto:matt-sheehan@outlook.com}{matt-sheehan@outlook.com}\\
  \href{https://mattsheehan.dev/}{https://mattsheehan.dev} & Mobile : 330-614-1599 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheadingWorkplace{Planet DDS}{Akron, OH}
    
  \resumeSubheadingPosition{Staff Software Engineer}{Feb 2023 - Present}
    \resumeItemListStart
      \resumeItem{Patient Engagement Platform}
        {Architected and lead a team of 3 onshore and 5 offshore developers to build a cloud native enterprise grade patient engagement system with a focus on high scalability to exceed our target throughput of 1 million customized SMS and Email messages per day.}
      \resumeItem{Tiger Team}
        {Lead a cross-functional team of 7 developers and 1 infrastructure engineer to tackle mission critical stability and reliabilty concerns following several major incidents affecting our flagship practice management software. After our work we were able to exceed our 99.5\% uptime SLA.}
      \resumeItem{Coding Standards}
        {Designed, documented, and implemented department coding standards. Worked with 5 different teams to implement style guidelines and encourage a unit-testing culture.}
    \resumeItemListEnd

  \resumeSubheadingPosition{DevOps Lead}{Jan 2022 - Feb 2023}
    \resumeItemListStart
      \resumeItem{Cloud Architecture}
        {Collaborated on designing a secure cloud-native architecture for moving flagship Denticon Practice Management product lines from on-premises to Azure and migrating Apteryx Imaging product lines to an enterprise-scale Azure architecture.}
      \resumeItem{Infrastructure as Code}
        {Standardized Bicep as company-wide Infrastructure as Code language for the transition to Azure. Provided standardized modules for infrastructure engineers to use that ensured cloud resources met our security policies.}
      \resumeItem{Mentoring Developers}
        {Mentored and assisted a department of over 50 developers modernizing the tech stack for each product line. Provided training on best practices for their migration to Azure from the datacenter.}
    \resumeItemListEnd

  \resumeSubheadingPosition{Senior Software Engineer}{[Acquired] Jan 2021 - Jan 2022}
    \resumeItemListStart
      \resumeItem{DICOM Capture}
        {Desktop application for capturing digital radiographs and patient data as DICOM files, transferring and storing data to a cloud PACS server. Integrates with multiple intra-oral device SDKs.}
      \resumeItem{Continuous Integration}
        {Automate build artifacts with Azure Pipelines for deployments of core web applications to staging environments.}
      \resumeItem{Private Package Feeds}
        {Developed private NPM and Nuget packages that could be consumed by multiple teams and projects.}
      \resumeItem{Hiring and Onboarding}
        {Conducted technical interviews and assessments for developers and collaborated on mentorship and onboarding processes for new employees.}
    \resumeItemListEnd

    % \resumeSubheading
    %   {Planet DDS}{Akron, OH}
    %   {DevOps Lead}{Jan 2022 - Present}
    %   \resumeItemListStart
    %     \resumeItem{Cloud Architecture}
    %       {Collaborated on designing a secure cloud-native architecture for moving flagship Denticon Practice Management product lines from on-premises to Azure and migrating Apteryx Imaging product lines to an enterprise-scale Azure architecture.}
    %     \resumeItem{Coding Standards}
    %       {Designed, documented, and implemented department coding standards. Standardized Bicep as company-wide Infrastructure as Code language for the transition to Azure.}
    %     \resumeItem{Mentoring Developers}
    %       {Mentored and assisted a department of over 60 developers modernizing the tech stack for each product line.}
    %   \resumeItemListEnd

    % \resumeSubheading
    %   {Planet DDS}{Akron, OH}
    %   {Senior Software Engineer}{[Acquired] Jan 2021 - Jan 2022}
    %   \resumeItemListStart
    %     \resumeItem{DICOM Capture}
    %       {Desktop application for capturing digital radiographs and patient data as DICOM files, transferring and storing data to a cloud PACS server. Integrates with multiple intra-oral device SDKs.}
    %     \resumeItem{Continuous Integration}
    %       {Automate build artifacts with Azure Pipelines for deployments of core web applications to staging environments.}
    %     \resumeItem{Private Package Feeds}
    %       {Developed private NPM and Nuget packages that could be consumed by multiple teams and projects.}
    %     \resumeItem{Hiring and Onboarding}
    %       {Conducted technical interviews and assessments for developers and collaborated on mentorship and onboarding processes for new employees.}
    %   \resumeItemListEnd
      
    \resumeSubheading
      {LED Medical Diagnostics / Apteryx Imaging, Inc}{Akron, OH}
      {Senior Software Engineer}{[Acquired] Jan 2017 - Jan 2021}
      \resumeItemListStart
        \resumeItem{Systems Status}
          {Service for providing customer support the current operational status of customer software at a glance.}
        \resumeItem{Automated Billing System}
          {Lead project for implementing the internal systems and architecture for the company-wide customer billing system and portal. Included features to automate monthly billing invoices and integrated with the company Active Directory Domain authentication. Leveraged Azure Functions to update each customer's bill, determined by storage usage and software licenses issued.}
        \resumeItem{Database Management Dashboard}
          {Core service to setup and deploy app databases and storage containers for cloud software on Azure. Used to manage over two-thousand corporate customer databases and track individual usage.}
        \resumeItem{Native Bridge Service}
          {Designed and implemented the desktop service to enable the company's legacy desktop software to interoperate with their PACS cloud software, including the development of three browser extensions (Chrome, Firefox, Microsoft Edge).}
      \resumeItemListEnd
      
    \resumeSubheading
      {Lock3 Software, LLC}{Akron, OH}
      {Software Engineer}{Jan 2018 - Jun 2018}
      \resumeItemListStart
        \resumeItem{Research and Programming Language Design}
          {Researched working draft Technical Specifications for C++ modules, contracts, allocators, concepts, and their implementations in modern C++ compilers, to determine their business utility and criteria for large C++ projects.}
      \resumeItemListEnd

    \resumeSubheading
      {Apteryx, Inc}{Akron, OH}
      {Software Engineer}{May 2013 - Jan 2017}
      \resumeItemListStart
        \resumeItem{OEM Software Customization}
          {Created the framework that allowed the company to OEM (Original Equipment Manufacture) their cloud imaging software to other software resellers, including the ability to include or exclude specific feature sets.}
        \resumeItem{Image Processing}
          {Researched and implemented custom image enhancements on digital x-rays for dentistry.}
        \resumeItem{Azure Deployment and Environment}
          {Created a testing, staging, and production deployment pipeline. Setup a CDN (Content Delivery Network) to host and deliver shared custom scripts. Responsible for deploying the company SaaS software and maintaining a consistent production environment while keeping a regular update schedule.}
        \resumeItem{Library Development}
          {Developed and maintained the core client-side libraries for all the company's web applications, including their flagship cloud imaging software (\footnotesize{XVWeb}). \small{These libraries were consumed by the rest of the development team and controlled the user experience for all customers.}}
        \resumeItem{Windows App}
          {Developed Windows 8/8.1 companion app for viewing, manipulating, and enhancing digital x-rays.}
      \resumeItemListEnd

    \resumeSubheading
      {Alliance Computer Exchange}{Alliance, OH}
      {Computer Repair Technician}{Aug 2011 - Dec 2012}
      \resumeItemListStart
        \resumeItem{Website Design}
          {Redesigned the company website.}
        \resumeItem{Computer Repair}
          {Performed technical assessments and serviced customer computers.}
        \resumeItem{Recycling}
          {Disassembled computers, printers, and other electronics to recycle the individual components.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
    \resumeSubHeadingListStart
        \resumeSubItem{Technologies}
          {Programmed in technologies including .NET 6-8, .NET Core, .NET Framework, SQL Server, DICOM, WebGL, React, Docker, Kubernetes, Microservices, and Azure Infrastructure Services.}
        \resumeSubItem{Languages}
          {Experience in C\#, Typescript, Javascript, SQL, C++, and Java.}
        \resumeSubItem{Tools}
          {Efficient with Git, Mercurial, Visual Studio Code, Visual Studio 20XX, Docker, PowerShell, and Azure DevOps Services.}
        \resumeSubItem{Process}
          {Familiar with Agile, Scrum, and kanban workflows using Azure Boards, Jira, Trello, Confluence, Microsoft Teams, and Slack. }
    \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects \& Talks}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CodeMash Speaker}{\textit{\small Jan 2024}}
      {$\cdot$ Simplifying Microservices with Dapr}{}\vspace{-4pt}
    \resumeSubheading
      {Momentum DevCon Speaker}{\textit{\small Oct 2022}}
      {$\cdot$ Do You Want to Build a Browser Extension?}{}\vspace{-4pt}
    \resumeSubheading
      {StirTrek Speaker}{\textit{\small May 2022}}
      {$\cdot$ OWASP Top 10: 2021 Edition}{}\vspace{-4pt}
    \resumeSubheadingMultiline
      {CodeMash Speaker}{\textit{\small Jan 2022}}
      {$\cdot$ Making the most of your DevOps Artifacts}{}
      {$\cdot$ Consistent cloud environments with Infrastructure as Code}
    \resumeSubItem{Jekyll Plugins}
      {Static site plugin generators for Windows 10 live tiles and Typescript support.}
    \resumeSubItem{Personal Homepage}
      {Maintain multiple subdomains at mattsheehan.dev hosted on DigitalOcean and secured by LetsEncrypt.}
    % \resumeSubItem{Language Design}
    %   {Toy lisp interpreter, borrowing heavily from Scheme and Common Lisp, written in CSharp.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Microsoft Certified: Azure Cosmos DB Developer Specialty}{}
      {Certification Number: 9EDA42-B345EA}{Aug 2022}
    \resumeSubheading
      {Microsoft Certified: Azure Solutions Architect Expert}{}
      {Certification Number: 28V754-D72900}{Aug 2022}
    \resumeSubheading
      {Microsoft Certified: Azure Administrator Associate}{}
      {Certification Number: 3M2DBD-CA46A7}{June 2022}
    \resumeSubheading
      {Microsoft Certified: DevOps Engineer Expert}{}
      {Certification Number: 09A440-I1570E}{Dec 2021}
    \resumeSubheading
      {Microsoft Certified: Azure Developer Associate}{}
      {Certification Number: 8S7EBD-59D5F7}{May 2021}
    \resumeSubheading
      {University of Mount Union}{Alliance, OH}
      {Bachelor of Science, Pyschology;  GPA: 3.47}{Aug 2009 - May 2013}
  \resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd
%

%-------------------------------------------
\end{document}
